### 2016-08-24 Chapters/ContinuumSolvationModels.tex
Add some more stuff from notes scattered around

>>>>

\section{Boundary integral equations}\label{sec:BIE}

\subsection{Transmission problem}
We assume Euclidean space $\mathbb{R}^3$ to be partitioned into two
subdomains $\Omegai$ and $\Omegae$ sharing a boundary $\Gamma$.
We further assume that $\Omegai$ is a closed domain, entirely contained inside $\Omegae$.
The transmission problem is posed as follows:
\todo[inline]{Some consideration on suitable functional spaces and the metric thereof.}
\begin{subequations}\label{eq:transmission}
\begin{align}
  \Li u &= f_\mathrm{i} \,\, \text{in}\,\, \Omegai \label{eq:internal} \\
  \Le u &= f_\mathrm{e} \,\, \text{in}\,\, \Omegae \label{eq:external} \\
  [u] &= \ue - \ui = g_\mathrm{D} \,\, \text{on}\,\, \Gamma
  \label{eq:trace-jump} \\
[\partial_L u] &= \partiale u - \partiali u = g_\mathrm{N} \,\,
\text{on}\,\, \Gamma \label{eq:conormal-jump} \\
|u| &\leq C \|x \|^{-1} \,\,\text{for}\,\,\| x \|\rightarrow\infty
\label{eq:radiation}
\end{align}
\end{subequations}
where the jump conditions (eqs. \eqref{eq:trace-jump} and
\eqref{eq:conormal-jump}) are given in terms of Dirichlet and Neumann
data for the solution $u$. The jump conditions are expressed in terms of
trace operators for the solution $u$ and its conormal derivative. For
notational simplicity, will use the symbols $\partiale$ and $\partiali$
for the latter and only give it in explicit form when needed. Please
refer to the book by \citeauthor{Sauter2011} for further details. The
fundamental solutions, or Green's functions, for the elliptic
differential operators $\Li$ and $\Le$ will be denoted by $\Gi$ and
$\Ge$, respectively.

\subsection{Boundary integral operators}
We introduce the relevant boundary integral operators for the abovementioned
transmission problem. They are three of the four components of the Calder\'on projector.
For $v \in L^2(\Gamma)$, $x, y \in \Gamma$:\footnote{We can assume a less restrictive functional space, \ie a Sobolev space of fractional order.}
\begin{equation}
\begin{aligned}
(\bi{S}_\star v)(x) &= \int_\Gamma G_\star(x, y)v(y)\diff y \\
(\bi{D}_\star v)(x) &= \int_\Gamma \partial_{L_\star,y}G_\star(x, y)v(y)\diff y \\
(\bi{D}^\dagger_\star v)(x) &= \int_\Gamma \partial_{L_\star,x}G_\star(x, y)v(y)\diff y \\
\end{aligned}
\end{equation}
where $\star$ is a placeholder for the $\mathrm{i}$ or $\mathrm{e}$ subscript.

\begin{lemma}[Properties of the boundary integral operators]
  The integral operators introduced above enjoy the following
  properties~\autocite{Hsiao2008, Sauter2011}:
  \begin{enumerate}
      \item on $L^2(\Gamma)$ $\bi{S}_\star$ is self-adjoint,
        $\bi{D}^\dagger_\star$ is the adjoint operator of
        $\bi{D}_\star$.
      \item The commutation relations:
        \begin{alignat}{2}
          \bi{D}_\star\bi{S}_\star = \bi{S}_\star\bi{D}^\dagger_\star, \quad&
          \bi{S}_\star\bi{D}_\star = \bi{D}^\dagger_\star\bi{S}_\star
        \end{alignat}
        hold
      \item The operators:
        \begin{subequations}
          \begin{align}
   \bi{S}_\star &: H^{-\frac{1}{2}}(\Gamma) \rightarrow H^{\frac{1}{2}}(\Gamma) \\
   \bi{D}_\star &: H^{\frac{1}{2}}(\Gamma) \rightarrow H^{\frac{1}{2}}(\Gamma) \\
   \bi{D}^\dagger_\star &: H^{-\frac{1}{2}}(\Gamma) \rightarrow H^{-\frac{1}{2}}(\Gamma)
          \end{align}
        \end{subequations}
      \item The operator $\bi{S}_\star$ is coervice and admits a
        continuous inverse in the aforementioned Sobolev spaces.
      \item The operators $\lambda - \bi{D}_\star$ and $\lambda -
        \bi{D}^\dagger_\star$ with $\lambda \in (-2\pi, +\infty)$
        admit a continuous inverse in the aforementioned
        Sobolev spaces.
  \end{enumerate}
\end{lemma}

\subsection{Lemma of Integral Representation}
For the transmission problem \ref{eq:transmission} there holds:
\begin{itemize}
\item $\forall x \in \Omegai$
\begin{equation}
u = \bi{S}_\mathrm{i}(\partiali u)
- \bi{D}_\mathrm{i}(\ui) + \int_{\Omegai} \Gi f_\mathrm{i}\diff y
\end{equation}
\item $\forall x \in \Omegae$
\begin{equation}
u = -\bi{S}_\mathrm{e}(\partiale u)
+ \bi{D}_\mathrm{e}(\ue) + \int_{\Omegae}\Ge f_\mathrm{e}\diff y
\end{equation}
\item $\forall x \in \Gamma$
  \begin{equation}\label{eq:stat3}
    \frac{1}{2}\ui = \bi{S}_\mathrm{i}(\partiali u)
    - \bi{D}_\mathrm{i}(\ui) + \int_{\Omegai}\Gi f_\mathrm{i}\diff y
  \end{equation}
\item $\forall x \in \Gamma$
  \begin{equation}\label{eq:stat4}
    \frac{1}{2}\ue = -\bi{S}_\mathrm{e}(\partiale u)
    + \bi{D}_\mathrm{e}(\ue) + \int_{\Omegae}\Ge f_\mathrm{e}\diff y
  \end{equation}
\end{itemize}

\pagebreak
\section{IEFPCM}\label{sec:IEF}

Note that the figures refer to cases where the dielectric is supposed to
be homogeneous and isotropic. The derivation are, however, general and
do not assume homogeneity and isotropy.
The source charge densities are not assumed to be continuous, the
hypothesis that they are entirely supported in either of the internal or
external subdomains is however made:
\begin{alignat}{2}
  \Supp(\rhoi) \subseteq \Omegai, \quad& \Supp(\rhoe) \subseteq \Omegae
\end{alignat}

%%%% CASE 0

\subsection{Case 0: sources in a vacuum cavity inside a dielectric}

\begin{figure}[h!]
  \centering
  \includegraphics[width=.65\textwidth]{case0}
  \caption{Vacuum Cavity in dielectric with permittivity $\diel_\mathrm{e}>1$.
  Source charge density $\rho_\mathrm{i}$ inside the cavity
  ($\diel_\mathrm{i}=1$). \textcolor{red}{Regular IEF}}
  \label{fig:case0}
\end{figure}

This is the regular IEF as derived in:~\autocite{Cances1998}
\begin{subequations}
\begin{align}
  \nabla^2 u &= \rhoi \,\, \text{in}\,\, \Omegai \\
  \Le u &= 0 \,\, \text{in}\,\, \Omegae \\
  [u] &= \ue - \ui = 0 \,\, \text{on}\,\, \Gamma \\
[\partial_L u] &= \partiale u - \partiali u = 0 \,\,
\text{on}\,\, \Gamma \\
|u| &\leq C \|x \|^{-1} \,\,\text{for}\,\,\| x \|\rightarrow\infty
\end{align}
\end{subequations}

We introduce the following auxiliary potential:
\begin{equation}
  h(x) =
  \begin{cases}
    &\int_{\mathbb{R}^3}\Gi\rhoi(y)\diff y  \quad x \in \Omegai \\
    &\int_{\mathbb{R}^3}\Ge\rhoi(y)\diff y  \quad x \in \Omegae
  \end{cases}
\end{equation}
for which we have:\footnote{This can be checked by applying the
differential operators to the definition of $h$ and then swapping
differentiation and integration.}
\begin{equation}
  \begin{cases}
    \nabla^2 h &= \rhoi \,\, \text{in}\,\, \Omegai \\
    \Le h &= 0 \,\, \text{in}\,\, \Omegae
  \end{cases}
\end{equation}
We then define the \emph{reaction potential} as:
\begin{equation}
  \xi = u - h
\end{equation}
such that:
\begin{subequations}
\begin{align}
  \nabla^2 \xi &= 0 \,\, \text{in}\,\, \Omegai \\
  \Le \xi &= 0 \,\, \text{in}\,\, \Omegae \\
  -[\xi] &= [h] \,\, \text{on}\,\, \Gamma \\
  -[\partial_L \xi] &= [\partial_L h] \,\, \text{on}\,\, \Gamma
\end{align}
\end{subequations}
inside the cavity, the reaction potential can be represented by a
\emph{single layer potential}, \ie by an apparent surface charge (ASC):
\begin{equation}
  \xi_\mathrm{i} = \bi{S}_\mathrm{i}\sigma
\end{equation}

Applying Eqs. \eqref{eq:stat3} and \eqref{eq:stat4} of the Lemma of Integral
Representation to the reaction potential yields:
\begin{align}
  \frac{1}{2}\xi_\mathrm{i} &= \bi{S}_\mathrm{i}(\partiali \xi) -
  \bi{D}_\mathrm{i}(\xi_\mathrm{i}) \\
  -\frac{1}{2}\xi_\mathrm{e} &= \bi{S}_\mathrm{e}(\partiale \xi) -
  \bi{D}_\mathrm{e}(\xi_\mathrm{e})
\end{align}
in both cases the last term, including the integration over the entire
subdomain volume, drops out ($f_\mathrm{i} = 0 = f_\mathrm{e}$).
While use of Eq. \eqref{eq:stat4} on the auxiliary potential $h$ yields:
\begin{equation}
  -\frac{1}{2}h_\mathrm{e} =
  \bi{S}_\mathrm{e}(\partiale h) -
  \bi{D}_\mathrm{e}(h_\mathrm{e})
\end{equation}
Together with the jump conditions one obtains:
\begin{subequations}
  \begin{align}
    &\bi{S}_\mathrm{i}(\partiali \xi) - \bi{D}_\mathrm{i}(\xi_\mathrm{i})
    = \frac{1}{2}\xi_\mathrm{i} \label{eq:first} \\
    &\bi{S}_\mathrm{e}(\partiale \xi) - \bi{D}_\mathrm{e}(\xi_\mathrm{e})
    = -\frac{1}{2}\xi_\mathrm{e} \label{eq:second} \\
  &\bi{S}_\mathrm{e}(\partiale h) - \bi{D}_\mathrm{e}(h_\mathrm{e})
  = -\frac{1}{2}h_\mathrm{e} \label{eq:third} \\
  &\xi_\mathrm{i} - \xi_\mathrm{e} = h_\mathrm{e} - h_\mathrm{i}
  \label{eq:fourth} \\
  &\partiali \xi - \partiale \xi = \partiale h - \partiali h
  \label{eq:fifth}
  \end{align}
\end{subequations}

\begin{enumerate}
  \item Add Eqs. \eqref{eq:second} and \eqref{eq:third}:
    \begin{equation}
    \bi{S}_\mathrm{e}(\partiale \xi + \partiale h) -
    \bi{D}_\mathrm{e}(\xi_\mathrm{e} + h_\mathrm{e})
    = -\frac{1}{2}(\xi_\mathrm{e} + h_\mathrm{e})
    \end{equation}
  \item Exploit Eqs. \eqref{eq:fourth} and \eqref{eq:fifth} to
    eliminate the external traces and conormal derivatives:
    \begin{equation}
      \bi{S}_\mathrm{e}(\partiali \xi) + \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)\xi_\mathrm{i} =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Introduce the integral representation of
    $\xi_\mathrm{i}$:
    \begin{equation}
      \bi{S}_\mathrm{e}(\partiali \xi) + \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}\sigma =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Reorganize Eq. \eqref{eq:first}, using the commutation
    relation and the integral representation of $\xi_\mathrm{i}$:
    \begin{equation}
    \partiali \xi = \left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)\sigma
    \end{equation}
    such that:
    \begin{equation}
      \left[ \bi{S}_\mathrm{e}\left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)
      +
      \left(\frac{1}{2} - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
      \right]\sigma =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Employ the Dirichlet-to-Neumann (DtN) map to simplify
    the RHS. The DtN map is derived by applying Eq. \eqref{eq:stat3} to
    the Newton potential:
    \begin{equation}
      \phi(x) = (\bi{N}\rhoi)(x) = \int_{\mathbb{R}^3}\Gi\rhoi(y)\diff y
      = \left.h(x)\right|_{\Omegai}
    \end{equation}
    which is equal, in $\Omegai$, to the auxiliary potential $h(x)$.
    With this definition one has:
    \begin{equation}
      \frac{1}{2}\phi_\mathrm{i} =
      \bi{S}_\mathrm{i}(\partiali \phi) -
      \bi{D}_\mathrm{i}(\phi_\mathrm{i}) + \int_{\Omegai}\Gi\rhoi(y)\diff y
      =
      \bi{S}_\mathrm{i}(\partiali \phi) -
      \bi{D}_\mathrm{i}(\phi_\mathrm{i}) + \phi_\mathrm{i}
    \end{equation}
    eventually leading to the DtN map:
    \begin{equation}\label{eq:regular-DtN}
      \left(\frac{1}{2} - \bi{D}_\mathrm{i}\right)\phi_\mathrm{i}
      +\bi{S}_\mathrm{i}(\partiali \phi) = 0
    \end{equation}
  \item Having identified $\phi_\mathrm{i} \equiv h_\mathrm{i}$
    and $\partiali \phi \equiv \partiali h$ and employing the DtN map,
    Eq.\eqref{eq:regular-DtN}, one obtains the IEF-PCM equation:
    \begin{equation}\label{eq:regular-IEF}
      \left[ \bi{S}_\mathrm{e}\left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)
      +
      \left(\frac{1}{2} - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
      \right]\sigma =
      -\left[\left(\frac{1}{2}-\bi{D}_\mathrm{e}\right)
      -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
       \left(\frac{1}{2}-\bi{D}_\mathrm{i}\right)
      \right]\phi
    \end{equation}
    where the subscript $\mathrm{i}$ for the Newton potential $\phi$ has
    been dropped, given that it is continuous across the boundary
    $\Gamma$.
\end{enumerate}
The above proves the existence of a representation of the reaction
potential valid \emph{inside} the cavity in terms of an apparent surface
charge density. We do not prove the uniqueness of this solution and
refer the interested reader to the original paper.~\autocite{Cances1998}

In the code, the Green's functions are defined \emph{without} the $4\pi$
factors in the denominator. Instead of $\frac{1}{2}$ as coefficients to
the identity operator, one will then have $2\pi$:
\begin{equation}\label{eq:regular-IEF-2pi}
  \left[ \bi{S}_\mathrm{e}\left(2\pi + \bi{D}^\dagger_\mathrm{i}\right)
  +
  \left(2\pi - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
  \right]\sigma =
  -\left[\left(2\pi-\bi{D}_\mathrm{e}\right)
  -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
  \left(2\pi-\bi{D}_\mathrm{i}\right)
  \right]\phi
\end{equation}

\paragraph{Isotropic IEF}
From Eq. \eqref{eq:regular-IEF-2pi} we can derive the isotropic IEF,
the DPCM and the CPCM (by letting $\diel\rightarrow\infty$) equations.
For a homogeneous, isotropic dielectric with permittivity $\diel$ the
Green's function outside the cavity is simply given by scaling the one
inside:
\begin{equation}
  \Ge = \frac{1}{\diel|x-y|} = \frac{1}{\diel} \Gi = \frac{1}{|x-y|}
\end{equation}
leading to the boundary integral operators:
\begin{alignat}{2}
  \bi{S}_\mathrm{i} = \diel\bi{S}_\mathrm{e} = \bi{S}, \quad&
  \bi{D}_\mathrm{i} = \bi{D}_\mathrm{e} = \bi{D}
\end{alignat}
Eventually, one has:
\begin{equation}
  \left[ 2\pi \left(\frac{\diel+1}{\diel-1}\right)
  - \bi{D} \right]\bi{S}\sigma
  =
  -\left[2\pi-\bi{D}\right]\phi
\end{equation}

### 2016-08-24 Chapters/PaperSummary.tex
Add some more stuff from notes scattered around

\begin{figure}[!htb]
\centering
\scalebox{0.8}{\input{gfx/relapcm/algorithm.tikz}}
\caption[Modular approach to programming a \acs{PCM} functionality into an existing \acs{SCF} code.]{
  Schematic view of the implemented SCF algorithm. Computations/data in
  \textcolor{Blue}{blue} are on the \pcmsolver side, in
  \textcolor{Green}{green} on the \DIRAC side.
  }
\label{fig:algorithm}
\end{figure}

>>>>

\begin{figure}[!htb]
\centering
\scalebox{0.8}{\input{gfx/algorithm.tikz}}
\caption[Modular approach to programming a \acs{PCM} functionality into an existing \acs{SCF} code.]{
  Schematic view of the implemented SCF algorithm. Computations/data in
  \textcolor{Blue}{blue} are on the \pcmsolver side, in
  \textcolor{Green}{green} on the \DIRAC side.
  }
\label{fig:algorithm}
\end{figure}

\todo[inline]{Have a closer look at this. I think it needs to be updated for the discussion
on open source software that went down on JPC Lett. some time ago.
Also, acronyms should be properly set up and reference to stuff not included in the thesis
(time-dependent) removed.}
It should also be mentioned that this has been accepted (in some partial/modified form)
for publication as a proceeding:
\begin{enumerate}
\item
  \textbf{R. Di Remigio}, T. D. Crawford, and L. Frediani
  \\
  PCMSolver: an Application Programming Interface
  for the Polarizable Continuum Model
  \\
  Accepted for publication in the proceedings of the
  \emph{Producing High Performance and Sustainable Software for
  Molecular Simulation} workshop held at the 2015 Supercomputing
  Conference
\label{SC15}
\end{enumerate}

The growing complexity of quantum chemical program packages requires
that an appropriate strategy be devised to implement new features.
Scalability is of paramount importance, but it has become clear
that maintainability and extensibility of the code play an equally
important role in managing this growing complexity \cite{Wilson2014}.

The use of a \emph{modular programming paradigm} has been recognized as
beneficial in many other scientific computing contexts. New features are
isolated into libraries that can be accessed by host programs through a
well-defined \emph{application programming interface} (API).
Computational tasks are thus implemented into separate, independent and
interchangeable modules. These are \emph{developed} and \emph{tested}
independently of the particular host program in which they will be used
\cite{Dijkstra1968, Parnas1972}.  A well-defined API clearly delimits
the boundaries of the functionality offered, thus forcing a programming
style and standardisation of the functionality, eventually.

When coupled with \emph{open-source} licensing, modularity is a proper
step towards ensuring reproducibility of results from scientific
simulation software \cite{Gezelter2015}.
Open-source development can fully leverage the benefits
of widespread, cloud-based, free, code development services, such as
hosted distributed version control systems (DVCSs), continuous integration, code
coverage, static and dynamic code analyses, nightly regression testing,
public issue tracking, code review and so forth:
adoption of a modern code development workflow is easily within reach.

It is, of course, true that the above mentioned services are not
exclusive prerogatives of open-source projects.
However, an open review process of scientific software can often help
to establish
reproducibility, extensibility and sustainability of the software
ecosystem.
Open-source software, modular development of new functionalities
and full-fledged exploitation of DVCSs ensure a much larger scientific
impact. Third-parties can easily contribute to
the project: by improving the documentation, by reporting bugs or
by actively extending the codebase with new functionality.

The description of chemical phenomena in complex environments, such as
solutions or proteins, is as challenging as it is important
for an accurate prediction of a wide range of properties
\cite{Reichardt2010}. Quantum chemistry is nowadays a valuable
tool: its simulations can provide significant insight into complex
chemical phenomena \cite{Nobel1998, Nobel2013}.
The major challenge lies in providing a faithful, realistic, yet cost-effective
description of the environment of the molecule:
a molecule in solution can be represented by a quantum mechanical model
comprising a great number of atoms, thousands or more. Such a simulation would,
however, be impossible to carry out with the current state-of-the-art
computational resources.
Models must be devised to overcome the dimensionality ``disease'' and
the idea of introducing different approximation levels for different
parts of the system under study is particularly appealing, as it helps
our chemical understanding. This is the idea at the basis of
\emph{multiscale} models.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=.45\textwidth]{multiscale.jpg}
\end{figure}

\emph{Continuum} (or \emph{implicit}) models, deal explicitly
only with the degrees of freedom associated with the solute, while
replacing the solvent with a structureless continuum characterized by
its bulk properties \cite{Onsager1936}. Among these models, the \acl{PCM} (\acs{PCM})
is the most widespread and successful \cite{Tomasi2005, mennucci}.

The \acs{PCM} is also an ideal candidate for the creation of a solvation API.
Its input from and output to \emph{any} quantum chemistry code is
limited and well-defined.
This provides a natural API design: the API functions can be compared
\emph{vis-à-vis} with the working equations derived for the different
quantum chemical methods.

We will elucidate the design principles adopted in the development of our
\pcmsolver{} library: an \emph{open-source} API for the inclusion of the
PCM in \emph{any} quantum chemistry code \cite{PCMSolver}.  Use of our
API \emph{significantly} limits coding effort on the side of the host:
continuum solvation at the self-consistent field
(SCF) level of theory can be implemented in the host program almost out-of-the-box.  The module is
agnostic of the host code internals and is tested separately from it.

We will emphasize the role of the open-source licensing model and the
importance of the modern workflows adopted in our project.  The adoption
of \git as distributed version control system, \cmake for cross-platform builds and automatic
documentation deployment on \readthedocs simplify extensibility of the
module and promote third-party contributions to the code base, while
continuous integration and nightly testing offer an invaluable level of
confidence in the code.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=.5\textwidth]{pcmsolver-scheme}
\end{figure}

\pcmsolver currently offers the basic PCM functionality already
available in many widespread software packages, such as traditional
collocation solvers for isotropic media \cite{Tomasi2005}.  Some unique
functionalities are the wavelet Galerkin solvers on smooth molecular
surfaces \cite{Weijo2010, Bugeanu2015}, the Green’s
functions for spherical diffuse interfaces \cite{Mozgawa2015}
and the delayed, time-dependent (TD) solvers for real-time TDSCF
simulations \cite{Corni2015}.

Careful usage of the C++ object-oriented paradigm is the key to this
wide spectrum of functionalities. The library is in itself made of
modules, communicating by means of composition at the outermost
level of the design.
This allows us to mix languages internally: we currently have Fortran
and C modules alongside the main C++ structure.
Library internal classes balance the dynamic polymorphism offered by
inheritance and the static polymorphism offered by template programming
\cite{Alexandrescu2001, Sutter2004}.
Preeminent use of composition over inheritance keeps the coupling
between different modules as low as possible \cite{Gamma1994}.

As a final example of the power of our modular strategy, we will present
our recent work on different quantum chemistry program packages,
tackling both uncorrelated and correlated wave functions \cite{DALTON,
PSI4} and also including relativistic effects \cite{DIRAC14brief,
DiRemigio2014}.  In particular, our recent work-in-progess on a
variational reformulation of the polarizable continuum model--coupled
cluster (PCM-CC) algorithm \cite{Cammi2009, Lipparini2011, Caricato2010a} within the
\psicode{} program package will be presented with emphasis on possible
applications to the prediction of the optical properties of chiral
molecules in solution.

### 2016-08-24 FrontBackmatter/Notation.tex
Add some more stuff from notes scattered around

A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here:
\begin{table*}[!h]
\begin{tabular}{c l}
 $\bi{A}, \bi{D}, \ldots$ & integral operators over a closed subset of $\mathbb{R}^2$ \\
 $H, \varPhi, \ldots$ & first or second quantized $N$-electron operators \\
 $\vect{r}, \vect{r}^\prime, \ldots$ & position vectors in $\mathbb{R}^3$ \\
 $\vect{s}, \vect{s}^\prime, \ldots$ & position vectors in a closed subset of $\mathbb{R}^2$ \\
 $\vect{v}, \vect{q}, \ldots$ & vectors in an arbitrary vector space \\
 $\mat{K}, \mat{F}, \ldots$ & matrices in an arbitrary vector space \\
 $0_N, I_N$ & the zero and the identity in an $N$-dimensional vector space
\end{tabular}
\end{table*}

>>>>

A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here:
\begin{table*}[!h]
\begin{tabular}{c l}
 $\bi{A}, \bi{D}, \ldots$ & integral operators over a closed subset of $\mathbb{R}^2$ \\
 $H, \varPhi, \ldots$ & first or second quantized $N$-electron operators \\
 $\vect{r}, \vect{r}^\prime, \ldots$ & position vectors in $\mathbb{R}^3$ \\
 $\vect{s}, \vect{s}^\prime, \ldots$ & position vectors on a closed surface \\
 $\vect{v}, \vect{q}, \ldots$ & vectors in an arbitrary vector space \\
 $\mat{K}, \mat{F}, \ldots$ & matrices in an arbitrary vector space \\
 $0_N, I_N$ & the zero and the identity in an $N$-dimensional vector space
\end{tabular}
\end{table*}

### 2016-08-24 FrontBackmatter/Publications.tex
Add some more stuff from notes scattered around

\begin{enumerate}[label=\textbf{\Roman{*} },ref=\Roman{*}]

@@

The following proceeding is also part of the thesis:
\begin{enumerate}
\item
  \textbf{R. Di Remigio}, T. D. Crawford, and L. Frediani
  \\
  PCMSolver: an Application Programming Interface
  for the Polarizable Continuum Model
  \\
  Accepted for publication in the proceedings of the
  \emph{Producing High Performance and Sustainable Software for
  Molecular Simulation} workshop held at the 2015 Supercomputing
  Conference
\label{SC15}
\end{enumerate}

>>>>

\begin{enumerate}[label=\textbf{\Roman{*} }, ref=\Roman{*}]

@@
